%-------------------------
% Resume in Latex
% Author : Max Li
% Website: https://github.com/maxsarratt/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}



\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%----------------------------------------------------------------------------------------
%	ADJUST MARGINS
%----------------------------------------------------------------------------------------
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

%----------------------------------------------------------------------------------------
%	SECTIONS FORMATTING
%----------------------------------------------------------------------------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%----------------------------------------------------------------------------------------
%	CUSTOM COMMANDS
%----------------------------------------------------------------------------------------
\newcommand{\resumeItemTwo}[2]{
  \item{
    \textbf{#1}{: \small #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubItem}[2]{\resumeItemTwo{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------------------------------------------------------------------------
%	Ensure that generate PDF is machine readable/ATS parsable
%----------------------------------------------------------------------------------------
\input{glyphtounicode}
\pdfgentounicode=1

%----------------------------------------------------------------------------------------
%	DOCUMENT BEGIN
%----------------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%	HEADING SECTION
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \scshape Max Li} \\ \vspace{4pt}
    +(886) 978-632-991 {$\diamond$} Taipei, Taiwan \\ \vspace{4pt} \href{mailto:maxsarratt@gmail.com}{\underline{maxsarratt@gmail.com}} {$\diamond$} \href{https://www.linkedin.com/in/maxsarratt/}{\underline{linkedin.com/in/maxsarratt}} {$\diamond$} \href{https://github.com/maxsarratt}{\underline{github.com/maxsarratt}}
    \vspace{-8pt}
\end{center}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\section{Objective}
  \begin{flushleft}
    {Vision-driven professional with a 5+ year record of backend software development. Seeking full-time SDE opportunity to utilize my skills and abilities in a value-driven company that offers professional growth while being resourceful, innovative, and flexible, driving myself towards the development of cutting-edge technologies for the future technologic landscape.}
  \end{flushleft}
  
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}
      {Java, JavaScript, SQL, Go, HTML/CSS, TypeScript}
    \resumeSubItem{Database}
      {PostgreSQL, MySQL, MongoDB, Redis}
    \resumeSubItem{Technologies/Frameworks}
      {Linux, Git, Node.js, Docker, Kubernetes, JUnit}
      \resumeSubItem{Tools}
        {IntelliJ IDEA, Visual Studio Code, Amazon Web Services}
  \resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\section{Open-Source Contributions}
  \resumeSubHeadingListStart
    \resumeSubItem{Murmurations Services}
      {A microservice I built with Go and Kubernetes which helps to validate store profiles against schemas, and provides API for later aggregation. Currently, it has validated more than 10K store profiles. (Project link: \href{https://github.com/MurmurationsNetwork/MurmurationsServices}{\underline{github.com/MurmurationsNetwork/MurmurationsServices)}}}
    \resumeSubItem{Mutual Credit Communication System}
      {An API service I built with Go and Docker to enable a network of trusted individuals to pay each other without conventional money. It's been running continuously for 2 years, and more than thousands of individuals have traded with each other. (Project link: \href{https://github.com/ic3network/mccs-alpha-api}{\underline{github.com/ic3network/mccs-alpha-api)}}}
  \resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	INDUSTRIAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Industrial Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ic3.network}{Paris, France}
      {Software Engineer (Remote Work)}{May 2019 - Present}
      \resumeItemListStart
        \resumeItem{Examine performance bottlenecks on existing search mechanism, utilizing Elasticsearch to rewrite the implementation, ultimately increasing the query speed by 53\%.}
        \resumeItem{Devise and execute a continuous build-test-deployment (CI/CD) system using GitHub Actions to support weekly releases and out-of-cycle releases, increasing development efficiency by 30\%.}
        \resumeItem{Transform extracted data sources into a data warehouse, constructing dashboards in Grafana to analyze daily transaction metrics of a half-million users.}
      \resumeItemListEnd

    \resumeSubheading
      {Rspective}{Katowice, Poland}
      {Software Engineer (Remote Work)}{Nov 2018 - May 2019}
      \resumeItemListStart
        \resumeItem{Formulated a Node.js backend service and administered various advertising strategies, increasing 30\% of the exposure rate for each targeting advertisement.}
        \resumeItem{Collaborated with the product growth team of 15 people on highlight notifications based on user activities, improving audience targeting and increasing active user rate by 40\%.}
        \resumeItem{Fostered communication with the data science and DevOps teams, collaboratively evaluating and establishing a better solution for the image recognition system through different metrics, ultimately rescuing \$25K annual costs.}
        \resumeItem{Encouraged team members to adopt emerging standards for software application development architecture and tools.}
      \resumeItemListEnd

    \resumeSubheading
      {Maodou.io}{Beijing, China}
      {Junior Software Engineer}{Aug 2016 - Oct 2018}
      \resumeItemListStart
        \resumeItem{Drafted and initiated a large-scale web service using Node.js and MongoDB to support +100,000 of online learners 6 months after launch.}
        \resumeItem{Generated scripts for automation testing in order to improve team efficiency by 20\% and reduce the effort of more than 1,000 hours of manual testing.}
        \resumeItem{Succeeded in rapid application development, as well as the management of technological issues.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Microverse}{Remote}
      {Remote Full Stack Web Development Program}{Mar 2018 - Nov 2018}
    \resumeSubheading
      {National Cheng Kung University}{Tainan, Taiwan}
      {Bachelor of Science in Aerospace Engineering}{Sep 2012 - June 2016}
  \resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	DOCUMENT END
%----------------------------------------------------------------------------------------
\end{document}
